A parametric system for contour parallel variable width toolpath generation

### 2019-08-05 0_main.tex
make properties of significant regions into Lemmas
new figure on transitioning and lil rewording on bead count section
lil
rewrite beading strategy section and write beading interpolation
rewrite toolpath extraction section
lil: abstract: why bead width matters
new title

@@

	\usepackage{algpseudocode} % algorithmic
	\usepackage{algorithm} % wrapper for pseudocode to give a caption and label
	\newcommand{\pluseq}{\mathrel{+}=} %pluseq symbol

@@

@@

\title{A robust framework for variable extrusion width concentric toolpath generation}

@@

A naive strategy for densely filling the outlines of a layer determines the toolpaths by performing inward offsets from the outline shape of a constant width.
In the center of the outline shapes this naive strategy can result in underfill regions and overfill regions as wide as the nozzle size.
Some previous literature solves these overfill and underfill problems by locally extruding a small amount of material less or more.
However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size.
We propose a framework which allows to define beading strategies which distribute the overfill and underfill required in each region over nearby toolpaths, so that we considerably reduce the amount of extrusion toolpaths with extreme widths.

>>>>

	\usepackage{amsthm} % \begin{proof}
	\newtheorem{lemma}{Lemma}[section]
	\theoremstyle{definition}
	\newtheorem{definition}{Definition}[section]

@@

	\usepackage[noend]{algpseudocode} % algorithmic
	\usepackage{algorithm} % wrapper for pseudocode to give a caption and label

	\newcommand{\pluseq}{\mathrel{+}=} %pluseq symbol
	\usepackage{upgreek} % \uplambda

@@

	\newlength{\figwidth}
	\newlength{\figheight}

@@

%\title{A robust framework for variable extrusion width concentric toolpath generation}
\title{A parametric system for contour parallel variable width toolpath generation}

@@

A naive strategy for densely filling the outlines of a layer determines the toolpaths by performing inward offsets from the outline shape of a constant width.
In the center of the outline shapes this naive strategy can result in underfill regions and overfill regions as wide as the nozzle size.
Some previous literature solves these overfill and underfill problems by locally extruding a small amount of material less or more.
However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size, which are difficult to manufacture.
We propose a framework which allows to define beading strategies which distribute the overfill and underfill required in each region over nearby toolpaths, so that we considerably reduce the amount of extrusion toolpaths with extreme widths.
